\section{Day 17}
\subsection{Morning}
Went out with Borah yesterday.
It was nice, she said something about me not getting attached to things or persons.
She said I did not miss her, but that is not true.
I do miss her when she is not there. It bothers me that she is to busy for me.
Allright. I will try to make a database restore today.
Would be nice to have a working instance.
Then I should be able to import the users.
I don't think they know about hash functions here.
It should be noticed that DHIS2 is not being used as intended.
Taking shortcuts like importing users into the database makes the users of the system not involved in the process. Venuste said that some of CHW's did not have the chance to go to school. 
If we take the shortcut, users will not be involved and we'll miss this oppertunity.
The best way to go is to involve all users in the process. This is what is needed.
I think I know the problem now. DHIS2 is not being used as intended.
Therefore it does not work as it should.
Take the databases from last year. Four instances of the program for some reason.
This is why the problems are appearing.

It would be beneficial if the team had a specialist on databases. 
It is weird that all work could be stopped just cause one person is gone.

\subsection{After lunch}
I don't know what Randy's plan is, but I assume that after importing the users, we will have the data managers reset the password.
Alright, job well done. Got the users imported, I assume that it will be no problem doing ut again.
I will show Venuste how we import the users using postgres in a little while. 

\subsection{Back home}
Seriously, people at work just does not know what they are doing.
No buts, no explanation. If one is about to use a database called postgres.
One should know what it is and how it works. 
The overall database design is a good thing to understand, but really.
Being able to manipulate it and use it is the are a must.

I think now I understand. 