\section{Day 15}
Alright. Everyday frustrations. 
Internet is not working. Apparently it should take 30 minutes to update flash player.
The driver was only 30 minutes late today. That is hes only job. 
Drive from A to B. He also took a detour so that we could spend some more time driving.
My phone is not working as I paid for. 
Now I am using airtime in order to be connected to the internet.
This was before work. Now, at work things don't run.
Like the VISA, I told Felix that I did not have a VISA for my whole stay, why is it necessary for me to say that he should fix it? It is like people don't listen.
That is the essence of why things don't go the way it should.
I also had to buy coffee in order to get some.
Thing is. I don't think people understand if they are not able to provide for coffee, how can they really be trusted to provide a information system covering the entire nation.
And we need working chairs as well as working internet.
The problem is obvious, yet nobody is doing anything about it.
Stable power is still an issue if one wants everyday life to go around the way we want and that affects work. One cannot separate work from everything else.

\subsection{Before Lunch}
I've got some tasks that should be accomplished. 
\begin{itemize}
	\item Import the users in the excel file.
	\item Make the hierarchy so that it has 8 levels instead of 6.
\end{itemize}

Apparently it is not easy to get a the address of the MSH offices.
Let's take the time. 10:40. 10:50.

Alright. Now it is not possible to take advantage of technology if one does not get replies.
Google maps is almost not responding. It takes forever to sync my google drive.


Internet is the building blocks of network, if this is not working then everything else will not work. The signature for the SMPP protocol is still missing. And the virtual server is not running.
The guys at the National Data Center is still trying to update from some Ubuntu version to the latest. Lunch in 2 minutes.

\subsection{After Lunch}
Today I will deliver my passport to Felix so that he can extend my VISA. Then I have to change my airplane tickets so that I can go home. Looking forward to it actually.

Also I have to see what is wrong with my internet at MTN.
