\section{Day 26}
Today is going to be a short day.
A trip to the forest. Nyonge I think it is.

\subsection{Email brief}
No problem, hi Yusuf :)

We are trying to make a sms based reporting system that will collect data from about 45,000 community health workers.

The data that we collect are stock and distribution values of 12 essential drugs. Initially it was 10, but some where added later. This can be a problem since a sms message only contains 160 characters, but we will look into that later.

We have first tested with a local instance that receives sms messages with the "*/sms/testSMS.action" script.
After getting this to work with some test data we moved on to test with the sms gateway android application.
This was very usefull. We could send messages to the phone with our own numbers and see the data going into the system. This also allowed us to have a demo for the 'clients' were we sent some reports.. 

We are still waiting for a signature in order to test for real (with a SMPP gateway), but we are moving forward by using the android application, a server at the national datacenter and maybe a test village just outside Kigali.

We will be able to report by SMS on Friday next week which is 1 of 4 use cases/requirements.
The next one we will work on is getting feedback after reporting. This is a built in functionality in DHIS2, but I have not yet tested if it works properly. After that we want to send out reminders if reports are late, by SMS and Email, and finally produce some reports based on the reported data.