\section{Day 37}
\subsection{The memorial day}
Yesterday was the memorial day. April 7th.
I went to the stadium to watch some speaches and events.
Was really nice. The walk to remember started at the parliament and ended at the stadium.
Borah had some horror stories from the genocide.
Funny thing, Eric wanted me write something about the genocide. Maybe I should write something about that and see if he still wants me to write it.
\subsection{First morning in a while}
Alright, let's get some work done today.
I want to finish the application, upload the users to the server. The I have to start configure the SMS service.
I could set up my phone at the national data center, but that would mean that we won't have a phone to use here.
I think we should set up a test server right here. 
It's hard to make things work when we don't have access to the right networks. VPN might be the answer. 
If I set up a virtual private network with the server at the national data center, I will be able to connect my phone the the server.
That should do it.
\subsection{After VAST}
Been a long time, since I ate there, ate there.
Vast brings good lunch as allways. 
Now I just want this day to end.
Ugh, bored. Got some progress today, but nothing significant.
It would be a good idea to work some in the evening to. Maybe continue on my masters. 

And probably send a mail to Ellen asking if I can get the exstension on my masters :)
Not very long now. Should actually start today.

\subsection{Interviews}
I should start collecting data for my thesis. Shit....
