\chapter{Requirements Document}

\section{Context}
This requirements document is for setting up a environment for a SMS based reporting system with the DHIS2. The system should be able to support these four use cases.

\begin{enumerate}
	\item The users will be able to receive automated SMS and email notifications based on rules that compare database values.
	\item The users will be able to receive an automated reminder if a report is more than 4 days delayed.
	\item The users will be provided with a predefined format for reporting.
	\item If the user reports values that does not get processed, then he/she will receive a notification of what has happened and directions for necessary steps in order to complete the report.
\end{enumerate} 

\section{Setting up Testing Environment}

\subsection{Testing without phone}
\subsubsection{Operating System}
\subsubsection{Tomcat}
\subsubsection{DHIS2}
The hierarchy has to be at a village level. This is the level we want to be reporting on.
\subsubsection{Postgres}
\subsubsection{Dataelements}
When creating data elements we store the zero values.
\subsubsection{Testing Script}
http://localhost:8080/dhis2/sms/testSMS.action
\begin{tabular}{|c|c|c|}
\hline
\textbf{Number} \textbf{Name} & \textbf{SMS code} & \textbf{Description} \\
1 & Oral Contraceptive Progestative Distributed & PPD & ? \\
2 & Oral Contraceptive Progestative Stock & PPS & ? \\
3 & Oral Contraceptive Combined Distributed & PCD & ? \\
4 & Oral Contraceptive Combined Stock & PCS & ? \\
5 & Condom Distributed & CMD & ? \\
6 & Condom Stock & CMS & ? \\
7 & Injectables (DMPA) Distributed & DPD & ? \\
8 & Injectables (DMPA) Stock & DPS & ? \\
9 & Misoprostol Distributed & MPD & ? \\
10 & Misoprostol Stock & MPS & ? \\
11 & Primo Red Distributed & PRD & ? \\
12 & Primo Red Stock & PRS & ? \\
13 & Primo Yellow Distributed & PYD & ? \\
14 & Primo Yellow Stock & PYS & ? \\ 
15 & Zinc Distributed & ZND & ? \\
16 & Zinc Stock & ZNS & ? \\
17 & ORS Distributed & RSD & ? \\
18 & ORS Stock & RSS & ? \\
19 & Amoxicillin Distributed & AMD & ? \\
20 & Amoxicillin Stock & AMS & ? \\
21 & Mebendazole Distributed & MBD & ? \\
22 & Mebendazole Stock & MBS & ? \\
23 & Vitamin A Distributed & VAD & ? \\
24 & Vitamin A Stock & VAS & ? \\
25 & RDT Distributed & RDD & ? \\
26 & RDT Stock & RDS & ? \\
\hline
\end{tabular}

